\TheTitle

### 2016-04-24 linvis.tex
Final editing
Making final changes to text
Final positioning of images

Adding 2016 IEEEtran.cls and bst files for proper formatting of document and
references.

\newif\ifdraft
\drafttrue

\ifdraft
        \documentclass[conference, draftclsnofoot]{IEEEtran}
        \def\baselinestretch{1}
        \setlength{\marginparwidth}{2cm}
\else
        \documentclass[conference]{IEEEtran}
        \def\baselinestretch{1}
        \setlength{\marginparwidth}{2cm}

        % \documentclass[conferece, final]{IEEEtran}
\fi

@@

% Fix any bad-hyphenations here
\hyphenation{}

@@

        Current tools provide information about repositories through the directed
        acyclic graph (DAG), which is helpful for smaller projects. However with the
        scale and number of branches in the kernel the DAG becomes overwhelming very
        quickly.

@@

Git cannot store the date that a commit was merged into a branch due to the rebase
operation. A rebase can perform serveral changes to commits and merges. It may be
squashed with other commits, combining the effects of several commits into a single
commit. It may be dropped altogether, in which case the commit is no-longer merged.
It may be that the entire branch has simply been re-rooted to another position on
the DAG. Due to this, tools are unable to determine when a commit is merged. A user
may decide that it is important to be able to see only the commits contributing to a
given release, that is commits that were merged with the Linus-branch of the kernel
between two given dates. This operation is not possible without the collection of
additional data that is not provided by git. Git only enables users to see when a
commit was authored, not when it was merged into a branch.

@@

In this paper, we present our design decisions behind a web-based
tool\footnote{\url{http://li.turingmachine.org}} built around the tree-based model
instead of the DAG. Our tool provides information about the location of a given
commit in the respective merge tree, the files edited, the modules edited, and the
commit message for a given commit or merge. The tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit id. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

To our knowledge, we know of no git repository visualization systems that build
trees from the DAG provided by git. This may be because more information is required
to generate the trees than what is stored by git. Git uses a DAG model, which
enables history-altering actions, like rebases to occur, whereas older tools like
CVS and svn construct trees\cite{CVS2008} but do not work with history-altering
actions.

A server must sit and monitor the git repository as it changes over time to handle
the changes to history. Many of the visualization tools are designed for a
general-purpose approach, where any repository is directly usable without additional
information. Polling for this additional information makes the visualizer specific
to a repository or project.

@@

Gitk, Gitg, and other similar git repository visualization tools use the DAG as the
central organization model. This model is sufficient for smaller projects, providing
meaningful information; however, in larger projects, like the Linux kernel, the
branches become too tangled and too deep to derive any meaning from the DAG. Users
can interact with the DAG by going to the previous commit in the chain or jumping to
the parent merge. This suggests that Gitk and similar tools are designed for users
working from a given commit or leaf-node toward the root. With this model, it is
difficult for users to see what other commits are involved with a given merge.

@@

University of Maryland presented a treemap visualization
tool\footnote{\url{https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html}},
pictured in figure \ref{fig:treemap}, for displaying the file structure of a given
version of the kernel. Treemaps are good for visualizing the topology of shallow,
wide trees, making it a good candidate for displaying file systems. Treemaps are
limited in what information can be displayed. The information within the treemap
does not provide clear insight on what changes were made to the files in the given
release, only providing information on where the file is located within the file
system, that is they do no provide temporal information. File systems and the merge
tree of the kernel share many similarities, in both cases, they represent trees that
are wide and shallow, suggesting that a treemap could potentially work to visualize
the commit and merge structure of the kernel.

@@

The treemap design is also designed for working with data of differing types. In the
filesystem, there are many kinds of files. There are text files, scripts, images,
binary files, and other types. These can be given colours making differences stand
out. There is no obvious way to assign meaningful types to the commits such that all
the commits within a given merge do not all have the same colour, although a user
could be given a controller to colour by author or number of files edited.

@@

We root the tree with the merge made by Linus. Each merge may contain zero or more
children, which are other merges and commits. If a merge is cherry-picked or rebased
there will be no children as this information is lost when the rebase occurs.
Commits have no children and are always leaf nodes. The commits contains the
metadata for the changes made. This metadata includes the files changed, the lines
added and removed from each file, the author, the date the commit was merged into
the merge that led to being merged into the kernel, and the date the commit was
authored, the diff, and the commit log. Merges contain less metadata, only storing
the author of the merge, the log, the commit date, and the author date. The details
of the model are outlined by German \cite{German2015}.

@@

The first tool we implemented was a small command-line shell (figure
\ref{fig:shell}) that allows users to navigate through the commits and merges as one
might navigate through files and directories. A user could navigate toward the
leaves of the tree by using the \verb|cd| command followed by the commit id of the
next merge. The user could then navigate toward the root by issuing \verb|cd ../|,
as they would in a file system. Users can use \verb|ls| to view what commits and
merges exist in the current working merge, then use \verb|cat| to view the log
preview of a commit or \verb|more| to see the preview and how many lines were added
and removed from the files in the commit.

@@

We replace the command-line interface with a web-based tool. Creating a web-based
tool enables users to use the system without having to install additional software
or carry a large database, making it more accessible, more easily maintainable, and
platform independent. A web-based tool can utilize more interactive means of
navigation and provide better explanations of commits and merges than the
command-line interface.

@@

Searching allows a user to filter commits and merges that are irrelevant. The search
mechanism breaks down the results by release version. A user can further narrow down
the search range using the commit date range. The commit date refers to the date of
the creation of the top-level merge. The commits and merges that are returned may
have a commit date beyond the given range if they were merged by Linus within the
date range. A user may then provide a search text, filtering on the author name,
the commit id, or keyword from the log. Any part of the author name may show up in
the results, including searching by email address. The commit ID must be specified
from the first character to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches for a
commit id of `c26' in the 3.10 Linux kernel. We will use this commit for showing
each of the features of the tool.

@@

The first tab displays the full commit log. From this, a user is able to see what
they would see had they searched for the commit using git log. This doesn't provide
additional information to the other tools, but helps to complete the functionality
of our tool. The commit log provides a user with the information about the content
of the commit and who has signed-off on the commit to ensure that it is good
quality. The message for merges may also contain the information about the commits
that are being merged into a given merge. The information within these messages is
highly variable, and is completely dependent on the author's style. As the user
moves toward the top-level merge, the quality of these messages generally improves.

@@

The second tab is the files tab. This tab provides information on what files have
been edited, how many lines were added, and how many lines were removed in a given
commit. This functionality is similar to the other tools available. Our tree-based
design model allows us to extend this functionality to merges, which the other tools
are unable to show. When a file is edited multiple times from different commits
within a merge, we simply add the added and removed lines to the values already
stored, though this could be extended to use the diff information to determine when
a line has been replaced rather than incrementing the lines removed and the lines
added.

@@

The modules tab shows the modules that are contained within the commit. Modules are
not natively recognized by git, and are not going to be present in all repositories.
In the Linux repository, authors put the module they are working on in the one-line
preview of the log-message. We heuristically extract the module by taking all text
in the log preview of commits until the first colon.  Modules are logical partitions
of the information in the kernel. Depending on where the author was working, modules
can be general, such as ``bluetooth'' and ``wireless'', or can be quite specific for
individual hardware, such as ``ath9k\_hw'' and ``wl1251''. In a few cases, the
author of a commit does not correctly follow this format and the hueristic approach
fails. Like files, we are able to show what modules are edited in merges and
commits. The image in figure \ref{fig:modules} shows the modules for a commit. A
commit will only ever have one module that it is associated with, merges with more
than one child will have more.

Finally, we have the tree view tab. The tree view is designed for providing easy
navigation within a tree and providing a clear topological view of the branch off
the kernel. We have experimented with various tree designs to find a design that
allows for easy navigation and visualization of both large and small trees. We
discuss the various tree designs in section \ref{treeview_section}.

@@

The list tree viewer is in the form of nested lists, and is designed to more closely
model the tree hierarchy view found in file browsers. This tree only contains the
commits and merges that are within the subtrees of the current merge. A commit will
never have any items in this tree as it is a leaf. To accompany the tree, we include
breadcrumbs at the top of the page to enable a user to navigate both from the root
to the leaves and from a leaf to the root. The last item in the breadcrumb list is
the current commit, the previous item is the parent of the current commit, and the
first item is the root merge into the kernel.

@@

The Reingold-Tilford tree produces very nice results, creating an intuitive
representation of the tree. The representation has a clear notion of root and
leaves, and how to navigate in either direction.

@@

The bubble tree provides a very clear picture of where a commit is located in the
hierarchy. The currently selected commit or merge is colored red, while non-selected
merges use a shade of blue and commits use white. The depth of the blue colouring is
dependent on how deep in the hierarchy that node is. The root is the lightest blue,
and the contained merges are progressively darker.

@@

\evan{Is this section necessary?}

@@

Nginx is a high-performance, scalable HTTP and mail server. Started in 2002, the
project is much younger than the Apache project, and designed with massive
scalability and multi-processing in mind. Instead of using request-driven threading,
Nginx uses an event-driven architecture, making it more scalable, proving itself as
being the web server behind large sites like Netflix, Hulu, GitHub, Tumblr, and many
other popular sites\footnote{\url{http://wiki.nginx.org/Main}}.

Postgresql is our dbms of choice, providing fast and reliable results. There are
multiple reasons behind choosing postgresql over another dbms. The main reason being
that the dataset built by German et al. was generated from a postgresql database,
allowing us to import the data directly without any further conversions. The
secondary reason is that we are more familiar with postgresql than the other systems
available.

@@

The database itself is broken down into 5 main tables; commits, filesmod, logs,
pathtomerge, and releases. Commits contains most of the metadata for each commit, it
contains the author, the authored date, and committer, the commit date, a boolean
saying what is a merge, and the diff. Filesmod contains the information on what
files were modified for the commits. Since a file may be modified by multiple
commits, and a commit may be modifying multiple files, we can do one of two things
for the primary key. We could use both the filename and the commit id as the primary
key, but we just use an index. The filesmod table contains the filename, the commit
id, the number of lines added, and the number of lines removed. Trivially, it
contains the index, but that isn't necessary for anything beyond the primary key.
Logs contains the information for each commit log, this is the one-liner preview
message and the full message. Pathtomerge is the important table. Pathtomerge
contains the commit id, the number of merges between the commit and the top-level
merge with the kernel, the next merge in the merge path up to the top-level merge
with the kernel, the top-level merge into the kernel, and when it get merged into
the kernel. The information in this table must be generated periodically by the
server because we are unable to generate the tree structure correctly straight from
the information stored by git. Pathtomerge does not contain any top-level merges, as
these will never have a next merge in the tree, since we are only storing the
parents and not the children, storing the top-level merge is redundant and
unnecessary. The releases table stores the release information.  It contains the
version name, whether the version is a candidate release or a real release, the
previous version, the previous non-candidate release version the previous version
commit id, the previous non-candidate release version commit id, and the commit id
of this version. The version commit id represents the last top-level merge into the
version of the kernel. Using this and the commits table, we are able to determine
the release date of any version of the kernel. Then using the previous release date,
we can find the range of dates where valid top-level merges are found for that
version.

@@

Our tool provides mechanisms and visualizations that other tools are unable to
produce. Continuous mining of the repository\cite{German} provides more information
about how the repository is changing. It gives us the ability to see how commits are
being merged into the kernel, allowing us to more reliably build trees from the
snapshots of the repository.

@@

Our goal was to build a tool to enable maintainers to effectively navigate and pull
explanation of the changes performed to the kernel over the period of a release.
Achieving this goal includes removing information that does not pertain to the area
of the kernel that the user is interested in. In figure \ref{fig:dag_view} and
figure \ref{fig:tree_view}, we can visually compare the results returned from gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. The relevant information to this commit in both of these
figures is identical, but the presentation drastically changes our ability to
comprehend what we are seeing. The primary difference is the removal of irrelevant
information. In gitk (\ref{fig:dag_view}), the visualization results include commits
and merges from other components of the kernel, while our tool (\ref{fig:tree_view})
only includes the results that are specific to the component of the kernel that we
are interested in.

@@

The response for the tree is a single object. This object is the root node of the
tree, and may contain an object of children objects in the \verb|children| field,
which are in the same format as the root object. The children object uses the commit
id as the key.

@@

\begin{tabular}{ccl}
        Field name      & Data type & Description\\\hline
        \verb|cid|      & string    & Commit id\\
        \verb|name|     & string    & One-line log preview\\
        \verb|mlinus|   & string    & Root merge commit id\\
        \verb|author|   & string    & Author name and email\\
        \verb|mnext|    & string    & Parent merge commit id\\
        \verb|children| & object    & Object of tree objects\\
\end{tabular}

The file responses contain only the files that the selected merge or commit works
with. The response is a single object in the form of a tree. This object is the root
of the tree, and represents the current merge or commit. If the current position in
the tree is an inner node, the response will contain the child nodes in the
``children'' field, otherwise ``children'' will be an empty list. The full response
format for the file response looks like:

\begin{tabular}{lll}
        Field name & Data type & Description\\\hline
        \verb|cid| & string & Commit id\\
        \verb|mnext| & string & Parent merge commit id\\
        \verb|children| & list & List of tree objects\\
        \verb|files| & list of tuples&
        \footnotesize{
        \begin{tabular}{lc}
                \verb|Filename| & String\\
                \verb|Lines added| & uint\\
                \verb|Lines removed| & uint\\
        \end{tabular}}\\
\end{tabular}

@@

There is currently no functionality surrounding searching by filename. Users falling
under use-case 2 may know what file they are editing and try to determine how it may
work with the other commits and merges in the module. It is possible that a third
use-case may arise, where the user wants to determine all commits that effect a
given file. In both cases, bottom-to-top approach is applied.

@@

\nocite{*}
\bibliographystyle{plain}
\bibliography{citations}

>>>>

\newif\ifdraft
% \drafttrue

\ifdraft
        \documentclass[conference, draftclsnofoot, draft]{IEEEtran}
        \def\baselinestretch{1}
        \setlength{\marginparwidth}{2cm}
\else
        \documentclass[conference]{IEEEtran}
\fi

@@

% Fix any bad-hyphenations here
\hyphenation{contained}

@@

        Current tools provide information about repositories through the directed
        acyclic graph (DAG), which is helpful for smaller projects. However, with
        the scale and number of branches in the kernel the DAG becomes overwhelming
        very quickly.

@@

Git cannot store the date that a commit was merged into a branch due to the rebase
operation. A rebase can perform several changes to commits and merges. It may be
squashed with other commits, combining the effects of several commits into a single
commit. It may be dropped altogether, in which case the commit is no-longer merged.
It may be that the entire branch has simply been re-rooted to another position on
the DAG. Due to this, tools are unable to determine when a commit is merged. A user
may decide that it is important to be able to see only the commits contributing to a
given release, that is commits that were merged with the Linus-branch of the kernel
between two given dates. This operation is not possible without the collection of
additional data that is not provided by git. Git only enables users to see when a
commit was authored, not when it was merged into a branch.

@@

In this paper, we present our design decisions behind a web-based
tool\footnote{\url{http://li.turingmachine.org}} built around the tree-based model
instead of the DAG. Our tool provides information about the location of a given
commit in the respective merge tree, the files edited, the modules edited, and the
commit message for a given commit or merge. The tool allows users to apply various
filters, including the release version, along with a keyword or phrase from the log
preview, the name of the author, or the commit ID. The user can request all the
root-level merges containing a commit or merge that matches the query, or all
commits and merges that match the query.

@@

To our knowledge, we know of no git repository visualization tool that builds
trees from the DAG provided by git. This may be because more information is required
to generate the trees than what is stored by git. Git uses a DAG model, which
enables history-altering actions, like rebases to occur, whereas older tools like
CVS and svn construct trees\cite{CVS2008} but do not work with history-altering
actions.

A server must sit and monitor the git repository as it changes over time to record
the changes to history. Many of the visualization tools are designed for a
general-purpose approach, where any repository is directly usable without additional
information. Polling for this additional information makes the visualizer specific
to a repository or project.

@@

Gitk, Gitg, and other similar git repository visualization tools use the DAG as the
central organization model. This model is sufficient for smaller projects, providing
meaningful information; however, in larger projects, like the Linux kernel, the
branches become too tangled and too deep to derive any meaning from the DAG. Users
can interact with the DAG by going to the previous commit in the chain or jumping to
the parent merge. This suggests that Gitk and similar tools are designed for users
working from a given commit or leaf-node toward the root. With this model, it is
difficult for users to see what other commits are involved within a given merge.

@@

University of Maryland presented a treemap visualization
tool\footnote{\url{https://www.cs.umd.edu/hcil/millionvis/Treemap_Visualization_of_the_Linux_Kernel_2_5_33.html}},
pictured in figure \ref{fig:treemap}, for displaying the file structure of a given
version of the kernel. Treemaps are good for visualizing the topology of shallow,
wide trees, making it a good candidate for displaying file systems. Treemaps are
limited in what information can be displayed. The information within the treemap
does not provide clear insight into what changes were made to the files in the given
release. It only provides information on where the file is located within the file
system; they do not provide temporal information. File systems and the merge
tree of the kernel share many similarities, in both cases, they represent trees that
are wide and shallow, suggesting that a treemap could potentially work to visualize
the commit and merge structure of the kernel.

@@

The treemap is also designed for working with data of differing types. In the
filesystem, there are many kinds of files. There are text files, scripts, images,
binary files, and other types. These can be given colours making differences stand
out. There is no obvious way to assign meaningful types to the commits such that all
the commits within a given merge do not have the same colour, although a user
could be given a controller to colour by author or number of files edited.

@@

We root the tree with the merge made by Linus. Each merge may contain zero or more
children, which are other merges and commits. If a merge is cherry-picked or rebased
there will be no children as this information is lost when the rebase occurs.
Commits have no children and are always leaf nodes. The commits contains the
metadata for the changes made. This metadata includes the files changed, the lines
added and removed from each file, the author, the date the commit was merged into
the merge that led to being merged into the kernel, and the date the commit was
authored, the patch, and the commit log. Merges contain less metadata, only storing
the author of the merge, the log, the commit date, and the author date. The details
of the model are outlined by German \cite{German2015}.

@@

The first tool we implemented was a small command-line shell (figure
\ref{fig:shell}) that allows users to navigate through the commits and merges as one
might navigate through files and directories. A user could navigate toward the
leaves of the tree by using the \verb|cd| command followed by the commit ID of the
next merge. The user could then navigate toward the root by issuing \verb|cd ../|
as they would in a file system. Users can use \verb|ls| to view what commits and
merges exist in the current working merge, then use \verb|cat| to view the log
preview of a commit or \verb|more| to see the preview and how many lines were added
and removed from the files in the commit.

@@

We replace the command-line interface with a web-based tool. Creating a web-based
tool enables users to use the system without having to install additional software
or store a large database, making it more accessible, more easily maintainable, and
platform independent. A web-based tool can utilize more interactive means of
navigation and provide better explanations of commits and merges than the
command-line interface.

@@

Searching (figure \ref{fig:search}) allows a user to filter commits and merges that
are irrelevant. The search mechanism breaks down the results by release version. A
user can further narrow down the search range using the commit date range. The
commit date refers to the date of the creation of the top-level merge. The commits
and merges returned may have a commit date beyond the queried dates; the date-range
query refers to the date that the commit is finally merged into the kernel by Linus.
A commit may not be merged immediately, and in some cases may take years before
being applied. A user may then provide a search text, filtering by the author name,
the commit ID, or keyword from the log. Any part of the author name may show up in
the results, including searching by email address. The commit ID must be specified
from the first character to the last character. For example, the commit
`c267548755a184ef97301071300c1739a564e135' is returned when the user searches for a
commit ID of `c26' in the 3.10 Linux kernel. We will use this commit for showing
each of the features of the tool.

@@

The first tab displays the full commit log (figure \ref{fig:message}). From this, a
user is able to see what they would see had they searched for the commit using git
log. This doesn't provide additional information to the other tools, but helps to
complete the functionality of our tool. The commit log provides a user with the
information about the content of the commit and who has signed-off on the commit to
ensure that it is good quality. The message for merges may contain a summary of the
commits being merged.  The information within these messages is highly variable, and
is completely dependent on the author's style. As the user moves toward the
top-level merge, the quality of these messages generally improves.

@@

The second tab is the files tab (figure \ref{fig:files}). This tab provides
information on what files have been edited, how many lines were added, and how many
lines were removed in a given commit. This functionality is similar to the other
tools available. Our tree-based design model allows us to extend this functionality
to merges, which the other tools are unable to show. To find the number of lines
added to a file in a merge, we take the sum of the lines added to that file in each
of the children of that merge. We do the same for calculating the number of lines
removed. This could be extended to use the patch information to determine when a
line has been replaced rather than incrementing the lines added and removed.

@@

The modules tab (figure \ref{fig:modules}) shows the modules that are contained
within the commit. Modules are not natively recognized by git, and are not going to
be present in all repositories.  In the Linux repository, authors put the module
they are working on in the one-line preview of the log-message. We heuristically
extract the module by taking all text in the log preview of commits until the first
colon.  Modules are logical partitions of the information in the kernel. Depending
on where the author was working, modules can be general, such as ``bluetooth'' and
``wireless'', or can be quite specific for individual hardware, such as
``ath9k\_hw'' and ``wl1251''. In a few cases, the author of a commit does not
correctly follow this format and the hueristic approach fails. Like files, we are
able to show what modules are edited in merges and commits. The image in figure
\ref{fig:modules} shows the modules for a commit.  As commits have no children, they
will only have a single module; merges with more than one child will have more.

Finally, we have the tree view tab. The tree view is designed for providing easy
navigation within a tree and providing a clear topological view of the branch of the
main kernel. We have experimented with various tree designs to find a design that
allows for easy navigation and visualization of both large and small trees. We
discuss the various tree designs in section \ref{treeview_section}.

@@

The list tree viewer (figure \ref{fig:list_tree}) is in the form of nested lists,
and is designed to more closely model the tree view found in file browsers. This
tree only contains the commits and merges that are within the subtrees of the
current merge. A commit will never have any items in this tree as it is a leaf. To
accompany the tree, we include breadcrumbs at the top of the page to enable a user
to navigate both from the root to the leaves and from a leaf to the root. The last
item in the breadcrumb list is the current commit, the previous item is the parent
of the current commit, and the first item is the root merge into the kernel.

@@

The Reingold-Tilford tree (figure \ref{fig:tree})produces very nice results,
creating an intuitive representation of the tree. This illustrates a clear notion of
root and leaves, and how to navigate in either direction.

@@

The bubble tree (figure \ref{fig:bubble_tree}) provides a very clear picture of
where a commit is located in the hierarchy. The currently selected commit or merge
is colored red, while non-selected merges use a shade of blue and commits use white.
The depth of the blue colouring is dependent on how deep in the hierarchy that node
is. The root is the lightest blue, and the contained merges are progressively
darker.

@@

\evan{Is this section necessary? The tables are probably useful, but the rest... not
sure on}

@@

Nginx is a high-performance, open source, scalable HTTP and mail server. Started in
2002, the project is much younger than the Apache project, and designed with massive
scalability and multi-processing in mind. Instead of using request-driven threading,
Nginx uses an event-driven architecture, making it more scalable, proving itself as
being the web server behind large sites like Netflix, Hulu, GitHub, Tumblr, and many
other popular sites\footnote{\url{http://wiki.nginx.org/Main}}.

Postgresql is our dbms of choice, providing fast and reliable results. There are
multiple reasons behind choosing postgresql over another dbms. The main reason being
that the dataset built by German et al. was generated from a postgresql database,
allowing us to import the data directly without any further conversions.

@@

The database itself is broken down into 5 main tables; commits, filesmod, logs,
pathtomerge, and releases. Commits contains most of the metadata for each commit; it
contains the author, the authored date, and committer, the commit date, a boolean
saying what is a merge, and the patch. Filesmod contains the information on what
files were modified for the commits. Since a file may be modified by multiple
commits, and a commit may be modifying multiple files, we can do one of two things
for the primary key. We could use both the filename and the commit ID as the primary
key, but we just use an index. The filesmod table contains the filename, the commit
ID, the number of lines added, and the number of lines removed. Trivially, it
contains the index, but that isn't necessary for anything beyond the primary key.
Logs contains the commit log preview and full commit log. Pathtomerge is the
important table.  Pathtomerge contains the commit ID, the number of merges between
the commit and the top-level merge with the kernel, the next merge in the merge path
up to the top-level merge with the kernel, the top-level merge into the kernel, and
the date it is merged into the kernel. The information in this table must be
generated periodically by the server because we are unable to generate the tree
structure correctly straight from the information stored by git. Pathtomerge does
not contain any top-level merges, as these will never have a next merge in the tree;
since we are only storing the parents and not the children, storing the top-level
merge is redundant and unnecessary. The releases table stores the release
information.

It contains
\begin{itemize}
        \item Version name
        \item Candidate releases versus real releases
        \item Previous release
        \item Previous real release
        \item Previous release commit ID
        \item Previous real release commit ID
        \item Current version commit ID
\end{itemize}
The current version commit ID represents the last top-level merge into the version
of the kernel. Using this and the commits table, we are able to determine the
release date of any version of the kernel. Then using the previous release date, we
can find the range of dates where valid top-level merges are found for that version.

@@

Our tool provides mechanisms and visualizations that other tools are unable to
produce. Continuous mining of the repository provides more information about how the
repository is changing. It gives us the ability to see how commits are being merged
into the kernel, allowing us to more reliably build trees from the snapshots of the
repository.

@@

Our goal was to build a tool to enable maintainers to effectively navigate and pull
an explanation of the changes performed to the kernel over the period of a release.
Achieving this goal includes removing information that does not pertain to the area
of the kernel that the user is interested in. In figure \ref{fig:dag_view} and
figure \ref{fig:tree_view} we can visually compare the results returned from gitk
and our tool for the top-level merge ``042dd60ca6dec9a02cefa8edd67de386e35755d6''
from kernel version 3.10. The relevant information to this commit in both of these
figures is identical, but the presentation drastically changes our ability to
comprehend what we are seeing. The primary difference is the removal of irrelevant
information. In gitk (\ref{fig:dag_view}), the visualization results include commits
and merges from other components of the kernel, while our tool (\ref{fig:tree_view})
only includes the results that are specific to the component of the kernel that we
are interested in.

@@

The response for the tree is a single object. This object is the root node of the
tree, and may contain an object of children objects in the \verb|children| field,
which are in the same format as the root object. The children object uses the commit
ID as the key.

@@

\begin{tabular}{ccl}
        Field name      & Data type & Description\\\hline
        \verb|cid|      & string    & Commit ID\\
        \verb|name|     & string    & One-line log preview\\
        \verb|mlinus|   & string    & Root merge commit ID\\
        \verb|author|   & string    & Author name and email\\
        \verb|mnext|    & string    & Parent merge commit ID\\
        \verb|children| & object    & Object of tree objects\\
\end{tabular}

The file responses contain only the files that the selected merge or commit works
with. The response is a single object in the form of a tree. This object is the root
of the tree, and represents the current merge or commit. If the current position in
the tree is an inner node, the response will contain the child nodes in the
``children'' field, otherwise ``children'' will be an empty list. The format of file
response is as follows,

\begin{tabular}{lll}
        Field name & Data type & Description\\\hline
        \verb|cid| & string & Commit ID\\
        \verb|mnext| & string & Parent merge commit ID\\
        \verb|children| & list & List of tree objects\\
        \verb|files| & list of tuples&
        \footnotesize{
        \begin{tabular}{lc}
                \verb|Filename| & string\\
                \verb|Lines added| & uint\\
                \verb|Lines removed| & uint\\
        \end{tabular}}\\
\end{tabular}

@@

There currently is no functionality surrounding searching by filename. Users falling
under use-case 2 may know what file they are editing and try to determine how it may
work with the other commits and merges in the module. It is possible that a third
use-case may arise, where the user wants to determine all commits that effect a
given file. In both cases, bottom-to-top approach is applied.

@@

\nocite{*}

\bibliographystyle{IEEEtran}
\bibliography{citations}
